Topic categorization in Portuguese news articles\\ \thanks{Fundação para a Ciência e Tecnologia}

### 2018-01-03 article.tex
Execution times

\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{float}
\usepackage{textcomp}
\usepackage{listings}
\usepackage{hyperref}
\usepackage[T1]{fontenc}
\usepackage[utf8x]{inputenc}
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
\begin{document}

@@

We used the \texttt{removeSparseTerms} function from the \texttt{tm}
package, and produced three distinct lists of terms:
\begin{description}
    \item[$TS_{99}$] contained the terms with a sparcity level below 99\% (912 terms)
    \item[$TS_{95}$] contained terms whose sparcity was under 95\% (139 terms)
    \item[$TS_{90}$] contained terms with 90\% or less sparcity (45 terms)
\end{description}

@@

We trained each of the classifiers three different times, one for each
list of terms ($TS_{99}$, $TS_{95}$ and $TS_{90}$). Then we evaluated
each trained classifier using the test dataset.

@@

\begin{table}[htbp]
    \caption{Error rates obtained for each algorithm and each list of
    terms}
\begin{center}
\begin{tabular}{l|rrrrrr}
                 & DT            & KNN           & NB   & NN   & SVM\textsubscript{RK} & SVM\textsubscript{LK} \\ \hline
    $TS_{90}$    & \textbf{0.60} & 0.71          & 0.85 & 0.61 & 0.88                  & 0.88                  \\
    $TS_{95}$    & 0.70          & \textbf{0.56} & 0.83 & 0.58 & 0.87                  & 0.87                  \\
    $TS_{99}$    & 0.70          & \textbf{0.35} & 0.87 & 0.76 & 0.87                  & 0.87                  \\
\end{tabular}
\label{error}
\end{center}
\end{table}
\begin{table}[htbp]
    \caption{Categories confusion matrix (k-nearest neighbors)}
\begin{center}
\begin{tabular}{l|rrrrrrrr}
& \rotatebox{75}{ciencia} & \rotatebox{75}{cultura} &
    \rotatebox{75}{desporto} & \rotatebox{75}{economia} &
    \rotatebox{75}{mundo} & \rotatebox{75}{musica} &
    \rotatebox{75}{pais} & \rotatebox{75}{politica} \\\hline
ciencia       & \textbf{64} & 18          & 25           & 29           & 21          & 37           & 4           & 2 \\
cultura       & 4           & \textbf{37} & 16           & 9            & 19          & 107          & 3           & 5 \\
desporto      & 1           & 4           & \textbf{130} & 8            & 19          & 35           & 2           & 1 \\
economia      & 0           & 6           & 9            & \textbf{127} & 12          & 32           & 1           & 13 \\
mundo         & 9           & 8           & 25           & 31           & \textbf{82} & 32           & 1           & 12 \\
musica        & 0           & 6           & 1            & 1            & 0           & \textbf{180} & 0           & 1 \\
pais          & 8           & 15          & 24           & 42           & 17          & 64           & \textbf{14} & 16 \\
politica      & 1           & 8           & 7            & 36           & 19          & 24           & 3           & \textbf{102} \\

\end{tabular}
\label{confmat}
\end{center}
\end{table}

@@

@@

André Santos has a scholarship from Fundação para a
Computação Científica Nacional.

>>>>

\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{float}
\usepackage{booktabs}
\usepackage{textcomp}
\usepackage{listings}
\usepackage{hyperref}
\usepackage{siunitx}
\usepackage[T1]{fontenc}
\usepackage[utf8x]{inputenc}
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
\begin{document}

@@

We used the \texttt{removeSparseTerms} function from the \texttt{tm}
package, and produced three distinct lists of terms:
\begin{description}
    \item[$LT_{90}$] contained terms with 90\% or less sparcity
    \item[$LT_{95}$] contained terms whose sparcity was under 95\%
    \item[$LT_{99}$] contained the terms with a sparcity level below 99\%
\end{description}

@@

For the process of training a

We trained each of the classifiers three different times, one for each
list of terms ($LT_{99}$, $LT_{95}$ and $LT_{90}$). Then we evaluated
each trained classifier using the test dataset.

@@

Table~\ref{tab:size} presents the size of each list of terms after
removing the

\begin{tabular}{S[table-format=3.0]}
\toprule
{Heading} \\
\midrule
1 \\
10 \\
100 \\
\bottomrule
\end{tabular}

\begin{table}[htbp]
    \caption{Lists size}
\begin{center}
\begin{tabular}{l|SS}
    & \parbox{6em}{\centering Sparsity\\threshold (\%)}  &
    \parbox{5em}{\centering Number\\of terms}   \\\hline
    $LT_{90}$ &  90                 &  45 \\
    $LT_{95}$ &  95                 & 139 \\
    $LT_{99}$ &  99                 & 912 \\
\end{tabular}
\label{tab:size}
\end{center}
\end{table}

Table~\ref{tab:error} presents the error rates obtained for each list
of terms using each of the classifiers, with the value of the best
classifier for each list highlighted in bold.

\begin{table}[htbp]
    \caption{Error rates}
\begin{center}
\begin{tabular}{l|rrrrrr}
                 & DT            & KNN           & NB   & NN   & SVM\textsubscript{RK} & SVM\textsubscript{LK} \\ \hline
    $LT_{90}$    & \textbf{0.60} & 0.71          & 0.85 & 0.61 & 0.88                  & 0.88                  \\
    $LT_{95}$    & 0.70          & \textbf{0.56} & 0.83 & 0.58 & 0.87                  & 0.87                  \\
    $LT_{99}$    & 0.70          & \textbf{0.35} & 0.87 & 0.76 & 0.87                  & 0.87                  \\
\end{tabular}
\label{tab:error}
\end{center}
\end{table}

Table~\ref{tab:exectime} presents the execution time for training the
algorithm with the lowest error rate for each list of terms.

\begin{table}[htbp]
    \caption{Execution times for training}
\begin{center}
\begin{tabular}{lcr}
                 & Algorithm  & Execution time \\\hline
    $LT_{90}$    & DT         & 12s  \\
    $LT_{95}$    & KNN        &  3m  \\
    $LT_{99}$    & KNN        & 57m  \\
\end{tabular}
\label{tab:exectime}
\end{center}
\end{table}

Table~\ref{tab:confmat} presents the confusion matrix generated using
the k-nearest neighbors classifier with the $LT_{99}$ list of therms,
with the number of correct classifications for each category
highlighted in bold.

\begin{table}[htbp]
    \caption{Categories confusion matrix ($LT_{99}$ with KNN)}
\begin{center}
\begin{tabular}{l|rrrrrrrr}
& \rotatebox{75}{ciencia}    & \rotatebox{75}{cultura}  &
    \rotatebox{75}{desporto} & \rotatebox{75}{economia} &
    \rotatebox{75}{mundo}    & \rotatebox{75}{musica}   &
    \rotatebox{75}{pais}     & \rotatebox{75}{politica} \\\hline
ciencia  & {\bf 127} & 19        & 1          & 6         & 12       & 24        & 11       & 0 \\
cultura  & 5         & {\bf 102} & 2          & 2         & 3        & 79        & 6        & 1 \\
desporto & 1         & 3         & {\bf  168} & 7         & 3        & 14        & 4        & 0 \\
economia & 5         & 3         & 0          & {\bf 146} & 5        & 17        & 14       & 10 \\
mundo    & 12        & 12        & 7          & 17        & {\bf 90} & 35        & 16       & 11 \\
musica   & 0         & 2         & 0          & 0         & 2        & {\bf 184} & 1        & 0 \\
pais     & 9         & 9         & 9          & 19        & 15       & 31        & {\bf 88} & 21 \\
politica & 1         & 3         & 0          & 30        & 8        & 17        & 14       & {\bf 127} \\
\end{tabular}
\label{tab:confmat}
\end{center}
\end{table}

@@

Looking to the error rate obtained in each of tests performed, we can
conclude that the best option was to use the largest list of terms
($LT_{99}$) and the k-nearest neighbors classifier.

@@

André Santos has a PhD scholarship from Fundação para a Ciência e
Tecnologia.
